Two-Party State Channels with State Assertions

### 2019-01-14 paper/main.tex
Missing 'on'

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
	\item Our state channel is also the first to ensure the cost of progressing an application is based only the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}

>>>>

\begin{itemize}
	\item We propose the first state channel that ensures an honest party never pays the cost to send the application's full state during the dispute process.
	\item Our state channel is also the first to ensure the cost of progressing an application is based only on the number of transactions required to reach a terminal state, thus it is independent of the application's computational cost.
	\item We provide a proof of concept implementation and experimentally demonstrate that it is cost-effective to deploy. 
\end{itemize}
